Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance

### 2024-04-18 paper/paper.qmd
Added Model Section

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
library(here)
library(gridExtra)

@@

### Model justification

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
library(here)
library(gridExtra)
library(modelsummary)

@@

\begin{align} 
ESG_i|\pi_i &\sim \mbox{Negative Binomial}(r, \pi_i) \\
logit(\pi_i) &= \beta_0 + \beta_1 \text{funds}_i + \beta_2  \text{fund\_size}_i + \beta_3 \text{IRR}_i +\beta_4 \text{staff}_i+\beta_5 \text{average\_fund\_size}_i \\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
\beta_5 &\sim \mbox{Normal}(0, 2.5)
\end{align}

## Model justification

Negative binomial regression offers a robust approach to analyzing count data, especially when the assumption of equal mean and variance, inherent to Poisson regression, is violated. This regression model accommodates overdispersion, a common characteristic in count data where the variance exceeds the mean, providing a more flexible framework than the Poisson model. In this paper, the negative binomial regression is employed to examine the relationship between firm characteristics and their ESG scores. Given the potential for overdispersion in these counts, the negative binomial regression provides a suitable and robust approach to our analysis.

@@

```{r}
#| label: tbl-3
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Results"
#| tbl-pos: H

#### Read data ####
analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")

### Model data ####

esg_model <- stan_glm(
  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
  data = analysis_data,
  family = neg_binomial_2(link = "identity"),
  seed = 555
)

modelsummary(esg_model)
